Light inextensible strings (thread) under tension in the Schwarzschild geometry

### 2021-01-25 string_physics_educator.tex
mention thread to avoid confusion with quantum string theory
typo

\title{Light inextensible strings under tension in the Schwarzschild geometry}

@@

\address{School of Engineering, Computing, and Mathematical Sciences, Auckland Iniversity of Technology, 55 Wellesley Street East\\
Auckland 1142, New Zealand
\email{hankin.robin@gmail.com}}

>>>>

\title{Light inextensible strings (thread) under tension in the
  Schwarzschild geometry}

@@

\address{School of Engineering, Computing, and Mathematical Sciences, Auckland University of Technology, 55 Wellesley Street East\\
Auckland 1142, New Zealand
\email{hankin.robin@gmail.com}}
